\TitleText

### 2019-08-18 dantzig_selector/presentation_B/3_proof.tex
Presentation: Fix minor error

\I \Emph{Q2}: Dantzig Selector requires the measurement matrix to observe restricted isometry property (more below), but is it true for \m {\M {P}}, and for what \Emph {design} of \m {\M {F}_B, \M {F}_R, \M {W}_B, \M {W}_R}?

@@

\I \Emph{Q4}: Cand\`es and Tao showed the Big-O error bound in terms of (in our notation) \m {N_H}, but does, for practical values, the algorithm converges for \Emph {high probability}?
}
% % % % % % % % % % % % % % % % % % % % % % % % % %
\Frame {Restricted Isometry Property}
{
\I \m {\V {g}} is called \Emph {\m {s}-sparse}, if only \m {s} of its components are nonzero.

@@

\I Set shorthand, for any unit vector \m {\V{u}},
\Disp {
\NC \rho := \NC \VNm {\M{P} \V{u}}_2^2 \NR
}
}
% % % % % % % % % % % % % % % % % % % % % % % % % %
\Frame {Proof Strategy}
{
\I Show that \m {\V{g}} is almost sparse

@@

\I Establish that \m {\M{P}} satisfies RIP for what probability

\I Take into consideration how \m {\V{g}} is not exactly sparse
}
% % % % % % % % % % % % % % % % % % % % % % % % % %
\Frame {\m {\V{g}} is Almost Sparse}
{
\I Call the vector of largest-magnitude \m {N_H L} positions of \m {\V{g}} to be \m {\V{g}_A}, and remaining positions of \m {\V{g}} to be \m {\V{g}_K}, so that \m {\V{g}_A +\V{g}_K =\V{g}}

\I We can show that 
\Disp {
\NC \V{g}_K
\leq R
:=\m {\F{1}{3 \R{N_H}}} \NR
}

\I \m {R \to 0} as \m {N_H \to \infty}
}
% % % % % % % % % % % % % % % % % % % % % % % % % %
\Frame {Concentration Inequality}
{

@@

\I Our task is reduced into establishment of the inequality!
}
% % % % % % % % % % % % % % % % % % % % % % % % % %
\Frame {Design of Beamformers}
{
\I Considering \Emph {Q2}: If each entry of \m {\M {P}} is i.i.d., then it's likely that, by whatever variation of Central Limit Theorem,
\Disp {
\NC \MB {E} \SB {\rho ^{k}}
\approx \NC 1
\quad \Ss {in distribution} \NR
}

@@

\I Try to set each entry of \m {\M{F}_B} (resp.\ \m {\M{W}_B}) to be i.i.d.\ Standard Complex Normal, multiplied by a design constant \m {\l_B >0} (so that the magnitude follows Rayleigh distribution).

\I And let each entry of \m {\M{F}_R} (resp.\ \m {\M{W}_B}) be uniformly distributed on the unit circle on the complex plane, multiplied by a design constant \m {\l_B >0}.
}
% % % % % % % % % % % % % % % % % % % % % % % % % %
\Frame {Chernoff Inequality}
{
\I Imitating the Chernoff Inequality argument in classical probability, we have, for any \m {s >0} so that, supposedly, both sides \m {< \infty},
\Disp {
\NC p
= \NC \MB{P} \SB {\rho \geq \RB {1 +\e} \MB{E} \SB {\rho}} \NR
\NC =\NC \MB{P} \SB {\Ss {e} ^{s \rho} \geq \Ss {e} ^{s \RB {1 +\e}}} \NR
\NC \leq \NC \Ss {e} ^{-s \RB {1 +\e}} \MB{E} \SB {\Ss {e} ^{s \rho}} \NR
}

@@

\I This motivates
\Disp {
\NC \l_B
=\NC \F {1} {\R {N_Y}},
\l_R
=\F {1} {\R {N_R}} \NR
}

\I So that
\Disp {
\NC \MB{E} \SB {\rho}
=\NC 1
}
}
% % % % % % % % % % % % % % % % % % % % % % % % % %
\Frame {Finding the Second Moment}
{
\I We can show that, after tedius calculation,
\Disp {
\NC \MB{E} \SB {\rho ^2}
\leq \NC N_Y^4 N_R^4 \l_B^8 \l_R^8 \RB {1 +N_Y^{-2}} \D \VNm {\V{u}} _2 ^4 \NR
\NC = \NC \RB {1 +N_Y^{-2}} \NR
}
}
% % % % % % % % % % % % % % % % % % % % % % % % % %
\Frame {Bounding Higher Moments}
{
\I We can show that, after a lot applications of various inequalities,
\Disp {
\NC \MB{E} \SB {\rho ^k}
\leq \NC N_Y^{2k} N_R^{2k} \l_B^{4k} \l_R^{4k}
\D \G \SB {k +1}^2
\D \VNm {\V{u}} _2 ^k \NR
\NC = \NC \G \SB {k +1}^2 \NR
}
}
% % % % % % % % % % % % % % % % % % % % % % % % % %
\Frame {Try to Substite the Moments of \m {\rho}...}
{
\I Plugging into the Chernoff Inequality we have
\Disp {
\NC \log p
\leq \NC \Min {s >0} \Bigg [
  -\RB {1 +\F{1}{2} \e -\F{1}{8} \e^2} s \NR
  \NC \NC \FourQ +\log \RB{
    1
    +s \MB{E} \SB {\rho}
    +\F{s ^2} {2} \MB{E} \SB {\rho^2}
    +\dots
  }
\Bigg ] \NR
}

@@

\I But the remainder term of MGF, \m {\MB{E} \SB {\Ss {e} ^{s \rho}}}, seems to \Emph {diverge}!
\Disp {
\NC \sum_{k=3}^\infty \F{s ^k} {k!} \MB{E} \SB {\rho ^k}
\leq \NC \sum_{k=3}^\infty \F{s ^k} {k!} \G \SB {k +1}^2
= \sum_{k=3}^\infty k! \D s ^k
\to \infty \NR
}
}
% % % % % % % % % % % % % % % % % % % % % % % % % %
\Frame {Try Again for \m {\R {\rho}}...}
{
\I Take square roots on both sides so that \m {\sum_{k=3}^\infty s ^k} is finite for \m {s <1}.
\Disp {
\NC p
= \NC \MB{P} \SB {\rho \geq \RB {1 +\e} \MB{E} \SB {\rho}} \NR
\NC =\NC \MB{P} \SB {\Ss {e} ^{s \R {\rho}} \geq \Ss {e} ^{s \R {1 +\e}}} \NR
\NC \leq \NC \Ss {e} ^{-s \R {1 +\e}} \MB{E} \SB {\Ss {e} ^{s \R {\rho}}} \NR
}

\I The \m {1/2} and \m {3/2} moments can be bounded by Cauchy Inequality:
\Disp{
\NC \F{1}{\R{1+N_Y^{-2}}}
\leq \NC \MB{E} \SB {\R{\rho}}
\leq 1, \NR
\NC 1
\leq \NC \MB{E} \SB {\rho ^{3/2}}
\leq \R{1+N_Y^{-2}}, \NR
}
}
% % % % % % % % % % % % % % % % % % % % % % % % % %
\Frame {Confirming the Concentration Ineq.}
{
\I Thus, Minimizing for \m {s} we have, for any \m {\e >0},
\Disp {
\NC \NC \log p \NR
%
\NC =\NC \Min {s >0} \Bigg [
  -\RB {1 +\F{1}{2} \e -\F{1}{8} \e^2} s
  +\MB{E} \SB {\R{\rho}} s
  +\F{1}{2} \RB {\MB{E} \SB {\rho} -\MB{E} \SB {\R {\rho}}^2} s^2 \NR
  \NC \NC \FourQ +\F{1}{6} \RB {-3 \MB{E} \SB {\R {\rho}} \MB{E} \SB {\rho} +2\MB{E} \SB {\R{\rho}} ^3 +\MB{E} \SB {\rho ^{3/2}}} s^3
  +\dots
\Bigg ] \NR
%
\NC =\NC \Min {s >0} \SB{
  -\F{1}{2} \e s
  +\F{1}{2} N_Y^{-2} \RB {1 -N_Y^{-2}} s^2
  +N_Y^{-2} \RB {\F{1}{3} -\F{5}{24} N_Y^{-2}} s^3
} \NR
%
\NC =\NC -\F{\e^2 N_Y^2} {8} \NR
}
}
% % % % % % % % % % % % % % % % % % % % % % % % % %
\Frame {Confirming the Concentration}
{
\I The lower tail can be proved in the same way as upper tail.

\I Conbining we have
\Disp{
\NC \MB{P}
\SB {
  \Nm {\VNm {\M{P} \V{u}} _2 ^2 -\VNm {\V{u}} _2 ^2}
  \geq \e \VNm {\V{u}} _2 ^2
}
\leq \NC 2\exp \SB {-\F{N_Y^2}{8} \e^2} \NR
}
}
% % % % % % % % % % % % % % % % % % % % % % % % % %
\Frame {Expected Error of DS}
{
\I In answer of \Emph {Q3}, It can be checked that the generalization from real to complex does not affect the argument, but only loosen the bound by a multiple.

>>>>

\I \Emph{Q2}: Dantzig Selector requires the measurement matrix to observe restricted isometry property (more below), but is it true for \m {\M {P}}, and under what \Emph {design} of \m {\M {F}_B, \M {F}_R, \M {W}_B, \M {W}_R}?

@@

\I \Emph{Q4}: Cand\`es and Tao showed the Big-O error bound in terms of (in our case) \m {N_H}, but does, for practical values, the algorithm converges for \Emph {high probability}?
}
% % % % % % % % % % % % % % % % % % % % % % % % % %
\Frame {Restricted Isometry Property}
{
\I \m {\V {g}} is called \Emph {\m {s}-sparse}, if only \m {s} of its components are nonzero.

@@

\I Set shorthand, for any unit vector \m {\V{u}},
\Disp {
\NC \rho := \NC \VNm {\M{P} \V{u}}_2^2 \NR
}
}
% % % % % % % % % % % % % % % % % % % % % % % % % %
\Frame {Proof Strategy}
{
\I Show that \m {\V{g}} is almost sparse.

\I Take into consideration how not exactly sparse \m {\V{g}} is.

@@

\I Establish that \m {\M{P}} satisfies RIP for certain probability.
}
% % % % % % % % % % % % % % % % % % % % % % % % % %
\Frame {\m {\V{g}} is Almost Sparse}
{
\I Call the vector of largest-magnitude \m {N_H L} components of \m {\V{g}} to be \m {\V{g}_A}, and remaining components of \m {\V{g}} to be \m {\V{g}_K}, so that \m {\V{g}_A +\V{g}_K =\V{g}}.

\I We can show that 
\Disp {
\NC \VNm{\V{g}_K} _2
\leq R
:=\m {\F{1}{3 \R{N_H}}}. \NR
}

\I Note that \m {R \to 0} as \m {N_H \to \infty}
}
% % % % % % % % % % % % % % % % % % % % % % % % % %
\Frame {Concentration Inequality}
{

@@

\I Our task is reduced into establishment of the inequality!
}
% % % % % % % % % % % % % % % % % % % % % % % % % %
\Frame {Design of Beamformers}
{
\I Considering \Emph {Q2}: If each entry of \m {\M {P}} is i.i.d., then it's likely that, by whatever variation of \m {Central Limit Theorem},
\Disp {
\NC \MB {E} \SB {\rho ^{k}}
\approx \NC 1
\quad \Ss {in\; distribution} \NR
}

@@

\I Try to set each entry of \m {\M{F}_B} (resp.\ \m {\M{W}_B}) to be i.i.d.\ Complex Standard Normal, multiplied by a design constant \m {\l_B >0} (so that the magnitude follows Rayleigh distribution).

\I And let each entry of \m {\M{F}_R} (resp.\ \m {\M{W}_R}) be uniformly distributed on the unit circle on the complex plane, multiplied by a design constant \m {\l_B >0}.
}
% % % % % % % % % % % % % % % % % % % % % % % % % %
\Frame {Chernoff Inequality}
{
\I Imitating the \Emph {Chernoff Inequality} argument in classical probability, we have, for any \m {s >0} so that, supposedly, both sides \m {< \infty},
\Disp {
\NC p
= \NC \MB{P} \SB {\rho \geq \RB {1 +\e} \MB{E} \SB {\rho}} \NR
\NC =\NC \MB{P} \SB {\Ss {e} ^{s \rho} \geq \Ss {e} ^{s \RB {1 +\e}}} \NR
\NC \leq \NC \Ss {e} ^{-s \RB {1 +\e}} \MB{E} \SB {\Ss {e} ^{s \rho}} \NR
}

@@

\I This motivates
\Disp {
\NC \l_B
=\NC \F {1} {\R {N_Y}},
\quad \l_R
=\F {1} {\R {N_R}} \NR
}

\I So that
\Disp {
\NC \MB{E} \SB {\rho}
=\NC 1
}
}
% % % % % % % % % % % % % % % % % % % % % % % % % %
\Frame {Finding the Second Moment}
{
\I We can show that, by tedius calculation,
\Disp {
\NC \MB{E} \SB {\rho ^2}
\leq \NC N_Y^4 N_R^4 \l_B^8 \l_R^8 \RB {1 +N_Y^{-2}} \D \VNm {\V{u}} _2 ^4 \NR
\NC = \NC \RB {1 +N_Y^{-2}} \NR
}
}
% % % % % % % % % % % % % % % % % % % % % % % % % %
\Frame {Bounding Higher Moments}
{
\I We can show that, with applications of various inequalities,
\Disp {
\NC \MB{E} \SB {\rho ^k}
\leq \NC N_Y^{2k} N_R^{2k} \l_B^{4k} \l_R^{4k}
\D \G \SB {k +1}^2
\D \VNm {\V{u}} _2 ^k \NR
\NC = \NC \G \SB {k +1}^2 \NR
}
}
% % % % % % % % % % % % % % % % % % % % % % % % % %
\Frame {Try to Substite the Moments of \m {\rho}...}
{
\I Plugging into the Chernoff Inequality we have
\Disp {
\NC \NC \log p \NR
\NC \leq \NC \Min {s >0} \SB {
  -\RB {1 +\e} s
  +\log \RB{
    1 +s \MB{E} \SB {\rho}
    +\F{s ^2} {2} \MB{E} \SB {\rho^2} +\dots
  }
} \NR
}

@@

\I But the remainder term of MGF, \m {\MB{E} \SB {\Ss {e} ^{s \rho}}}, seems to \Emph {diverge}!
\Disp {
\NC \sum_{k=3}^\infty \F{s ^k} {k!} \MB{E} \SB {\rho ^k}
\leq \NC \sum_{k=3}^\infty \F{s ^k} {k!} \G \SB {k +1}^2
= \sum_{k=3}^\infty k! \D s ^k
\to \infty \NR
}
}
% % % % % % % % % % % % % % % % % % % % % % % % % %
\Frame {Try Again for \m {\R {\rho}}...}
{
\I Take square roots on both sides so that the remainder term is finite for \m {s <1}.
\Disp {
\NC p
= \NC \MB{P} \SB {\rho \geq \RB {1 +\e} \MB{E} \SB {\rho}} \NR
\NC =\NC \MB{P} \SB {\Ss {e} ^{s \R {\rho}} \geq \Ss {e} ^{s \R {1 +\e}}} \NR
\NC \leq \NC \Ss {e} ^{-s \R {1 +\e}} \MB{E} \SB {\Ss {e} ^{s \R {\rho}}} \NR
}

\I The \m {1/2} and \m {3/2} moments can be bounded by Cauchy Ineq.:
\Disp{
\NC \F{1}{\R{1+N_Y^{-2}}}
\leq \NC \MB{E} \SB {\R{\rho}}
\leq 1, \NR
\NC 1
\leq \NC \MB{E} \SB {\rho ^{3/2}}
\leq \R{1+N_Y^{-2}}, \NR
}
}
% % % % % % % % % % % % % % % % % % % % % % % % % %
\Frame {Confirming the Concentration Ineq.}
{
\I Thus, Minimizing for \m {s} we have, for any \m {\e >0},
\Disp {
\NC \NC \log p \NR
%
\NC =\NC \Min {s >0} \Bigg [
  -\RB {1 +\F{1}{2} \e -\F{1}{8} \e^2} s
  +\MB{E} \SB {\R{\rho}} s
  +\F{1}{2} \RB {\MB{E} \SB {\rho} -\MB{E} \SB {\R {\rho}}^2} s^2 \NR
  \NC \NC \FourQ +\F{1}{6} \RB {-3 \MB{E} \SB {\R {\rho}} \MB{E} \SB {\rho} +2\MB{E} \SB {\R{\rho}} ^3 +\MB{E} \SB {\rho ^{3/2}}} s^3
  +\dots
\Bigg ] \NR
%
\NC =\NC \Min {s >0} \SB{
  -\F{1}{2} \e s
  +\F{1}{2} N_Y^{-2} \RB {1 -N_Y^{-2}} s^2
  +N_Y^{-2} \RB {\F{1}{3} -\F{5}{24} N_Y^{-2}} s^3
} \NR
%
\NC =\NC -\F{\e^2 N_Y^2} {8} \NR
}
}
% % % % % % % % % % % % % % % % % % % % % % % % % %
\Frame {Confirming the Concentration}
{
\I The lower tail can be proved in the same way as upper tail.

\I Conbining we have
\Disp{
\NC \MB{P}
\SB {
  \Nm {\VNm {\M{P} \V{u}} _2 ^2 -\VNm {\V{u}} _2 ^2}
  \geq \e \VNm {\V{u}} _2 ^2
}
\leq \NC 2\exp \SB {-\F{N_Y^2}{8} \e^2} \NR
}
}
% % % % % % % % % % % % % % % % % % % % % % % % % %
\Frame {Expected Error of Dantzig Selector}
{
\I In answer of \Emph {Q3}, It can be checked that the generalization from real to complex does not affect the argument, but only loosen the bound by a multiple.

### 2019-08-18 dantzig_selector/presentation_B/5_conclusion.tex
Presentation: Fix minor error

\I We modified DS for present setting: for almost sparsity, in the angular domain, for the almost-sparse condition, for the beamformer matrix in our setting, and for complex vectors.

>>>>

\I We modified DS for present setting: for the almost-sparse condition, for the angular domain, for the beamformer matrix \m {\M {P}} in our setting, and for complex vectors.
